# Results


This is Figure \@ref(fig:plot-learner-accuracy-by-utterance-type)


(ref:plot-learner-accuracy-by-utterance-type) Response accuracy: Probability of a correct response for each utterance type in the logistic space.

```{r, 'plot-learner-accuracy-by-utterance-type', fig.cap="(ref:plot-learner-accuracy-by-utterance-type)"}
knitr::include_graphics(
  here("figs", "manuscript", "learner_accuracy_by_utterance_type.pdf")
  )
```




This is Figure \@ref(fig:plot-learner-accuracy-rt-by-speaker-variety)

(ref:plot-learner-accuracy-rt-by-speaker-variety) Response accuracy: Partially pooled estimates for each speaker variety.

```{r, 'plot-learner-accuracy-rt-by-speaker-variety', fig.cap="(ref:plot-learner-accuracy-rt-by-speaker-variety)"}
knitr::include_graphics(
  here("figs", "manuscript", "learner_accuracy_rt_by_speaker_variety.png")
  )
```





This is Figure \@ref(fig:plot-learner-accuracy-lt-eq-by-utterance-type)

(ref:plot-learner-accuracy-lt-eq-by-utterance-type) Response accuracy: Probability of a correct response in the logistic space as a function of LexTALE score (left panel) and empathy quotient (right panel) for each utterance type. Thin lines represent 300 draws from the posterior distribution for each condition.

```{r, 'plot-learner-accuracy-lt-eq-by-utterance-type', fig.cap="(ref:plot-learner-accuracy-lt-eq-by-utterance-type)"}
knitr::include_graphics(
  here("figs", "manuscript", "learner_accuracy_lt_eq_by_utterance_type.pdf")
  )
```









This is Figure \@ref(fig:plot-learner-accuracy-3way)

(ref:plot-learner-accuracy-3way) Response accuracy: Probability of a correct response as a function of empathy quotient and LexTALE score for each question type.

```{r, 'plot-learner-accuracy-3way', fig.cap="(ref:plot-learner-accuracy-3way)"}
knitr::include_graphics(
  here("figs", "manuscript", "learner_accuracy_3way.pdf")
  )
```






This is Figure \@ref(fig:plot-ddm-bs-dr-estimates)

(ref:plot-ddm-bs-dr-estimates) Need a caption.

```{r, 'plot-ddm-bs-dr-estimates', fig.cap="(ref:plot-ddm-bs-dr-estimates)"}
knitr::include_graphics(
  here("figs", "manuscript", "ddm_bs_dr_estimates.pdf")
  )
```




This is Figure \@ref(fig:plot-ddm-simulations)

(ref:plot-ddm-simulations) Two-thousand simulations of the drift diffusion model for interrogative utterances as a function of empathy quotient (low/high) and LexTALE score (low/high). Low and high levels represent &pm;2 standard deviations above/below the mean. Dark red lines represent the average decision time course.

```{r, 'plot-ddm-simulations', fig.cap="(ref:plot-ddm-simulations)"}
knitr::include_graphics(
  here("figs", "manuscript", "ddm_simulations.pdf")
  )
```
