# On-line supplementary material

## Drift diffusion models








```{=openxml}
<w:p><w:r><w:br w:type="page"/></w:r></w:p>
```

## Supplementary analyses


```{r, 'table-learner-accuracy-by-utterance-type'}
read_csv(here("tables", "learner_response_01.csv")) %>% 
  knitr::kable(format = "pandoc", align = c("l", "r", "r", "r", "r", "r"), 
    caption = "Summary of the posterior distribution modeling 
    response accuracy as a function of utterance type, LexTALE, and 
    Empathy quotient. The table includes posterior medians, the 95% HDI, 
    the percentage of the HDI within the ROPE, and the maximum probability 
    of effect (MPE).",
    label = "table-learner-accuracy-by-utterance-type")
```




This is Figure \@ref(fig:plot-sm-random-speaker-check)

(ref:plot-sm-random-speaker-check) Make sure each variety represented equally over course of experiment.

```{r, 'plot-sm-random-speaker-check', fig.cap="(ref:plot-sm-random-speaker-check)"}
knitr::include_graphics(
  here("figs", "manuscript", "sm_random_speaker_check.pdf")
  )
```

This is Figure \@ref(fig:plot-sm-random-speech-rate)

(ref:plot-sm-random-speech-rate) Make sure each variety represented equally over course of experiment.

```{r, 'plot-sm-random-speech-rate', fig.cap="(ref:plot-sm-random-speech-rate)"}
knitr::include_graphics(
  here("figs", "manuscript", "sm_speech_rate.pdf")
  )
```








```{=openxml}
<w:p><w:r><w:br w:type="page"/></w:r></w:p>
```

## Reproducibility information

**About this document**  

This document was written in RMarkdown using `papaja` [@R-papaja].

**Session info**  

```{r, session-info, comment=""}
devtools::session_info()$platform
as.data.frame(devtools::package_info())[, c(3, 8)]
```
