# On-line supplementary material

## Drift diffusion models








```{=openxml}
<w:p><w:r><w:br w:type="page"/></w:r></w:p>
```

## Learner accuracy

This section contains tables reported but not included in the main text. 
Table \@ref(tab:table-learner-accuracy-by-utterance-type) is equivalent to Figure ???

```{r, 'table-learner-accuracy-by-utterance-type'}
read_csv(here("tables", "learner_response_01.csv")) %>% 
  knitr::kable(format = "pandoc", align = c("l", "r", "r", "r", "r", "r"), 
    caption = "Summary of the posterior distribution modeling 
    response accuracy as a function of utterance type, LexTALE, and 
    Empathy quotient. The table includes posterior medians, the 95% HDI, 
    the percentage of the HDI within the ROPE, and the maximum probability 
    of effect (MPE).",
    label = "table-learner-accuracy-by-utterance-type")
```


Table \@ref(tab:table-ddm-bs-dr) is equivalent to Figure X in the main document. 

```{r, 'table-ddm-bs-dr'}
read_csv(here("tables", "ddm_bs_dr.csv")) %>% 
  mutate(Model = case_when(
    Model == "Boundary separation" & Parameter == "Intercept" ~ "Boundary", 
    Model == "Boundary separation" & Parameter == "Question type" ~ "separation", 
    Model == "Boundary separation" & !(Parameter %in% c("Intercept", "Question type")) ~ " ", 
    Model == "Drift rate" & Parameter == "Intercept" ~ "Drift rate", 
    Model == "Drift rate" & Parameter != "Intercept" ~ " ", 
  )) %>% 
  knitr::kable(format = "pandoc", align = c(rep("l", 2), rep("r", 5)), 
    caption = "Summary of the posterior distribution modeling 
    boundary separation and drift rate as a function of question type, 
    LexTALE, and Empathy quotient. The table includes posterior medians, 
    the 95% HDI, the percentage of the HDI within the ROPE, and the maximum 
    probability of effect (MPE).",
    label = "table-ddm-bs-dr")
```





## Supplementary analyses

In this section we present supplementary analyses, all of which are exploratory in nature. 
*D'*. Figure \@ref(fig:plot-learner-dp-utterance-variety) and Table \@ref(tab:table-dp-utterance-variety) represent an exploratory analysis of d' scores as a function of utterance type and speaker variety. 
One observes similar patterns to those from the accuracy analysis presented in the manuscript. 

(ref:plot-learner-dp-utterance-variety) Exploratory analysis of d' as a function of utterance type and speaker variety. Points represent posterior medians &pm;66% and 95% credible intervals.

```{r, 'plot-learner-dp-utterance-variety', fig.cap="(ref:plot-learner-dp-utterance-variety)"}
knitr::include_graphics(
  here("figs", "manuscript", "learner_dp_utterance_variety.pdf")
  )
```


```{r, 'table-dp-utterance-variety'}
read_csv(here("tables", "dp_utterance_variety.csv")) %>% 
  mutate(Model = case_when(
    Model == "Utterance type" & Parameter == "Declarative broad focus" ~ "Utterance type", 
    Model == "Utterance type" & Parameter != "Declarative broad focus" ~ " ", 
    Model == "Variety" & Parameter == "Andalusian" ~ "Variety", 
    Model == "Variety" & Parameter != "Andalusian" ~ " " 
  )) %>% 
  knitr::kable(format = "pandoc", align = c(rep("l", 2), rep("r", 3)), 
    caption = "Summary of the posterior distribution modeling 
    d' as a function of question type or speaker variety. The table 
    includes posterior medians, the 95% HDI, and the maximum 
    probability of effect (MPE).",
    label = "table-dp-utterance-variety")
```

*Randomization check across participants*. 

This is Figure \@ref(fig:plot-sm-random-speaker-check)

(ref:plot-sm-random-speaker-check) Make sure each variety represented equally over course of experiment.

```{r, 'plot-sm-random-speaker-check', fig.cap="(ref:plot-sm-random-speaker-check)"}
knitr::include_graphics(
  here("figs", "manuscript", "sm_random_speaker_check.pdf")
  )
```

*Speech rate*. This is Figure \@ref(fig:plot-sm-random-speech-rate)

(ref:plot-sm-random-speech-rate) Make sure each variety represented equally over course of experiment.

```{r, 'plot-sm-random-speech-rate', fig.cap="(ref:plot-sm-random-speech-rate)"}
knitr::include_graphics(
  here("figs", "manuscript", "sm_speech_rate.pdf")
  )
```








```{=openxml}
<w:p><w:r><w:br w:type="page"/></w:r></w:p>
```

## Reproducibility information

**About this document**  

This document was written in RMarkdown using `papaja` [@R-papaja].

**Session info**  

```{r, session-info, comment=""}
devtools::session_info()$platform
as.data.frame(devtools::package_info())[, c(3, 8)]
```
