# On-line supplementary material

## Drift diffusion models








```{=openxml}
<w:p><w:r><w:br w:type="page"/></w:r></w:p>
```

## Supplementary analyses

This is Figure \@ref(fig:plot-sm-random-speaker-check)

(ref:plot-sm-random-speaker-check) Make sure each variety represented equally over course of experiment.

```{r, 'plot-sm-random-speaker-check', fig.cap="(ref:plot-sm-random-speaker-check)"}
knitr::include_graphics(
  here("figs", "manuscript", "sm_random_speaker_check.pdf")
  )
```

This is Figure \@ref(fig:plot-sm-random-speech-rate)

(ref:plot-sm-random-speech-rate) Make sure each variety represented equally over course of experiment.

```{r, 'plot-sm-random-speech-rate', fig.cap="(ref:plot-sm-random-speech-rate)"}
knitr::include_graphics(
  here("figs", "manuscript", "sm_speech_rate.pdf")
  )
```








```{=openxml}
<w:p><w:r><w:br w:type="page"/></w:r></w:p>
```

## Reproducibility information

**About this document**  

This document was written in RMarkdown using `papaja` [@R-papaja].

**Session info**  

```{r, session-info, comment=""}
devtools::session_info()$platform
as.data.frame(devtools::package_info())[, c(3, 8)]
```
