---
title       : |
  Using intonation to disambiguate meaning: The role of empathy and proficiency in L2 perceptual development
authors     : "Joseph V. Casillas"
journal     : "Applied Psycholinguistics"
manuscript  : "APS-Feb-22-0015.R1"

bibliography: 
  - "../../../bib/empathy.bib"

output      : papaja::revision_letter_pdf
header-includes:
  - \usepackage{tipa}
  - \usepackage{booktabs}
  - \usepackage{hyperref}
  - \usepackage{longtable}
---

```{r}
#| label: setup
#| warning: false
#| message: false
library("papaja")
source(here::here("scripts", "r", "13_small_data.R"))
```

Dear Dr. Joan Mora, 


Thank you for taking the time to consider our manuscript _`r rmarkdown::metadata$title`_ (`r rmarkdown::metadata$manuscript`) for publication in _`r rmarkdown::metadata$journal`_. 
For the second round of revisions we have taken into consideration the suggestions from reviewer 2 and reviewer 3 and revised the manuscript accordingly. 
We believe the revisions, while minor in scope, have helped to make the manuscript stronger. 
In this letter we again address the reviewers' concerns point-by-point. 
Where feasible, we quote all revised text in this document, otherwise, we refer the reader to the relevant sections of the revised manuscript. 
We thank you and the anonymous reviewers for all comments and suggestions and again enthusiastically submit the revised manuscript for consideration in _`r rmarkdown::metadata$journal`_.


Sincerely,  
Joseph Casillas  
(corresponding author)

\clearpage

# Reviewer \#1

```{r}
#| child: "reviewer1.Rmd"
#| eval: TRUE
```

# Reviewer \#2

```{r}
#| child: "reviewer2.Rmd"
#| eval: TRUE
```

\clearpage

# Reviewer \#3

```{r}
#| child: "reviewer3.Rmd"
#| eval: TRUE
```

\newpage


# References

::: {#refs custom-style="Bibliography"}
:::
