---
title       : |
  Using intonation to disambiguate meaning: The role of empathy and proficiency in L2 perceptual development
authors     : "Joseph V. Casillas"
journal     : "Applied Psycholinguistics"
manuscript  : "APS-Feb-22-0015"

bibliography: 
  - "../../../bib/empathy.bib"

class       : "draft"
output      : papaja::revision_letter_pdf
header-includes:
  - \usepackage{tipa}
  - \usepackage{booktabs}
  - \usepackage{hyperref}
---

Dear XXX, 


Thank you for taking the time to consider our manuscript _`r rmarkdown::metadata$title`_ (`r rmarkdown::metadata$manuscript`) for publication in _`r rmarkdown::metadata$journal`_. 
Our understanding is that we needed to consider the reviewers' comments and revise accordingly before the manuscript could be reevaluated for publication.
We have considered thoroughly the detailed feedback provided by all three reviewers and resubmit what we believe to be a much improved version of the manuscript. 
In this letter we address the reviewers' concerns point-by-point. 
Where feasible, we quote all revised text in this document, otherwise, we refer the reader to the relevant lines in the revised manuscript. 
We thank you and the 3 anonymous reviewers for all comments and suggestions and again enthusiastically submit the revised manuscript for consideration in _`r rmarkdown::metadata$journal`_.


Sincerely,  
Joseph Casillas  
(corresponding author)

\clearpage

# Reviewer \#1

```{r, child="reviewer1.Rmd", eval = T}
```

\clearpage

# Reviewer \#2

```{r, child="reviewer2.Rmd", eval = T}
```

\clearpage

# Reviewer \#3

```{r, child="reviewer3.Rmd", eval = T}
```

<!--
\RC
This is a reviewer comment

This is our response

\Assignment{First Author}
\WorkInProgress
\Easy


\RC{This is the first paragraph of a long reviewer comment

This is the second paragraph}

This is our response.

> This is a section quoted from the revised manuscript to illustrate the change.

\Assignment{Second Author}
\AlmostDone
\Medium


\RC
This is a reviewer comment

This is our response

\Assignment{First Author}
\Done
\TimeConsuming
\Hard
\NotEstimated

-->

\newpage

# References

::: {#refs custom-style="Bibliography"}
:::
