---
title       : |
  Using intonation to disambiguate meaning: The role of empathy and proficiency in L2 perceptual development
authors     : "Joseph V. Casillas"
journal     : "Applied Psycholinguistics"
manuscript  : "APS-Feb-22-0015"

bibliography: 
  - "../../../bib/empathy.bib"

class       : "draft"
output      : papaja::revision_letter_pdf
header-includes:
  - \usepackage{tipa}
  - \usepackage{booktabs}
  - \usepackage{hyperref}
---

Dear XXX, 


Thank you for taking the time to consider our manuscript _`r rmarkdown::metadata$title`_ (`r rmarkdown::metadata$manuscript`) for publication in _`r rmarkdown::metadata$journal`_. 
Our understanding is that we needed to consider the reviewers' comments and revise accordingly before the manuscript could be reevaluated for publication.
We have considered thoroughly the detailed feedback provided by all three reviewers and resubmit what we believe to be a much improved version of the manuscript. 
In this letter we address the reviewers' concerns point-by-point. 
Where feasible, we quote all revised text in this document, otherwise, we refer the reader to the relevant lines in the revised manuscript. 
We thank you and the 3 anonymous reviewers for all comments and suggestions and again enthusiastically submit the revised manuscript for consideration in _`r rmarkdown::metadata$journal`_.


Sincerely,  
Joseph Casillas  
(corresponding author)

\clearpage

# Reviewer \#1

```{r, child="reviewer1.Rmd", eval = T}
```

\clearpage

# Reviewer \#2

```{r, child="reviewer2.Rmd", eval = T}
```

\clearpage

# Reviewer \#3

```{r, child="reviewer3.Rmd", eval = T}
```



\newpage

From @hualde2015intonational

Andalusian
  - @sosa1999
  - @henriksen2012transcription

Argentine
  - @sosa1999
  - @colantoni2004convergence
  - @colantoni2011broad
  - @labastia2006prosodic
  - @labastia2011procedural

Chilean
  - @lira2000prosodia
  - @ortiz2003acentos

Cuban
  - @sosa1999
  - @alvord2006spanish

Madrileño
  - @quilis1981 
  - @quilis1987 
  - @quilis1993
  - @sosa1999
  - @estebas_prieto2010

Mexican
  - @quilis1981 
  - @quilis1987 
  - @quilis1993
  - @sosa1999
  - @sosa2003
  - @butragueno2003hacia
  - @butragueno2004configuraciones

Peruvian
  - @sosa1999
  - @orourke2005intonation

Puerto Rican
  - @quilis1981 
  - @quilis1987 
  - @quilis1993
  - @sosa1999
  - @sosa2003
  - @armstrong2010puerto
  - @armstrong2012development


\newpage


# References

::: {#refs custom-style="Bibliography"}
:::
